\bf The EPEC Model

### 2021-09-26 Documentation/EPEC_Model.tex
Added Sphinx documetation

The quantities ${\mit\Delta}_k^{pw}$ and ${\mit\Sigma}_k^{\,pw}$
are defined as 
\begin{align}
{\mit\Delta}_k^{nw}&= \lim_{\delta\rightarrow 0}
\left[\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k+\delta}
- \left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k-\delta}\right],\\[0.5ex]
{\mit\Sigma}_k^{\,pw} &= \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k+\delta}+ \left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k-\delta}
-2\,A_k\,(1+\ln\delta)\right].
\end{align}
Here, $\psi_{pw}(r)$ is a solution of the cylindrical tearing mode equation that is well-behaved at $r=0$,
continuous at $r=r_k$, and satisfies 
\begin{equation}
\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_{100}} = -m\left[\frac{1+(r_{100}/r_w)^{\,2m}}{1-(r_{100}/r_w)^{\,2m}}\right].
\end{equation}
It is also helpful to define
\begin{align}
{\mit\Sigma}_{kw} &= \frac{2m\,(r_{100}/r_w)^{\,m}}{1-(r_{100}/r_w)^{\,2m}}\,\frac{\psi_{pw}(r_{100})}{\psi_{pw}(r_k)},\\[0.5ex]
{\mit\Delta}_{kw} &= -\frac{{\mit\Sigma}_{kw}^{\,2}}{{\mit\Delta}^{nw}_k-{\mit\Delta}^{pw}_k},\\[0.5ex]
B_k &= -\left(\frac{r^{\,2}\,q\,\hat{J}_\phi''}{s}\right)_{r_k},
\end{align}
where $\hat{J}_\phi'' \equiv d^2\hat{J}_\phi/dr^{\,2}$.

\section{Neoclassical Physics}\label{appb}
\subsection{Plasma Species}\label{a3}
The plasma is assumed to consist of three (charged) species; namely,  electrons ($e$), majority ions ($i$), and impurity ions
($I$).  The charges of the  three species are $e_e=-e$, $e_i= e$, and $e_I=Z_I\,e$, respectively, where
$e$ is the magnitude of the electron charge. 
Quasi-neutrality demands that
$n_e= n_i+ Z_I\,n_I$, where $n_a(r)$ is the species-$a$ number density. 
 Let 
$\alpha_I(r) =Z_I\,(Z_{\rm eff}-1)/(Z_I-Z_{\rm eff})$,
where 
$Z_{\rm eff}(r) = (n_i+Z_I^{\,2}\,n_I)/n_e$
is the effective ion charge number. It follows that
$n_i/n_e = (Z_I-Z_{\rm eff})/(Z_I-1)$
and
$n_I/n_e= (Z_{\rm eff}-1)/[Z_I\,(Z_I-1)]$. Finally, let $Z_{{\rm eff}\,i}= (Z_I-Z_{\rm eff})/(Z_I-1)$, and
$Z_{{\rm eff}\,I}=Z_I\,(Z_{\rm eff}-1)/(Z_I-1)$. Note that $Z_{\rm eff}= Z_{{\rm eff}\,i}+ Z_{{\rm eff}\,I}$.

@@

\section{Plasma Response in Inner Region}
\subsection{Linear Layer Widths}\label{linear}
Let
\begin{align}
\tau_R(r) &= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{ee},\\[0.5ex]
\sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
\tau_H(r) &= \frac{R_0}{B_0\,g}\,\frac{\sqrt{\mu_0\,\rho}}{n\,s},\\[0.5ex]
\tau_E(r) &= \frac{r^{\,2}}{D_\perp + (2/3)\,\chi_e},\\[0.5ex]
\tau_M(r) &= \frac{R_0^{\,2}\,q^{\,2}}{\chi_\phi},\\[0.5ex]
\rho_s (r)&= \frac{\sqrt{m_i\,T_e}}{e\,B_0\,g},\\[0.5ex]
\tau(r)& = -\frac{\omega_{\ast\,i}}{\omega_{\ast\,e}},\\[0.5ex]
S(r) &= \frac{\tau_R}{\tau_H},\\[0.5ex]
P_M(r) &= \frac{\tau_R}{\tau_M},\\[0.5ex]
P_E(r) &= \frac{\tau_R}{\tau_E},\\[0.5ex]
D(r)&= \frac{5}{3}\,S^{\,1/3}\,\frac{\rho_s}{r},\\[0.5ex]
Q_E(r)&= S^{\,1/3}\,n\,\omega_E\,\tau_H,\\[0.5ex]
Q_{e,i}(r)&= -S^{\,1/3}\,n\,\omega_{\ast\,e,i}\,\tau_H
\end{align}
Here, $\chi_e(r)$, $D_\perp(r)$, and $\chi_\phi(r)$ are the perpendicular electron energy, particle,
and toroidal momentum diffusivity profiles, respectively. 
The constant-$\psi$ linear layer width is determined from the solution of
\begin{equation}\label{e87}
\frac{d^{\,2}\,Y}{dp^{\,2}} -\left[\frac{-Q_E\,(Q_E-Q_i)+{\rm i}\,(Q_E-Q_i)\,(P_M+P_E)\,p^{\,2}+
P_M\,P_E\,p^{\,4}}
{{\rm i}\,(Q_E-Q_e) +\{P_E + {\rm i}\,(Q_E-Q_i)\,D^{\,2}\}\,p^{\,2}+(1+\tau)\,P_M\,D^{\,2}\,p^{\,4}}
\right] p^{\,2}\, Y = 0.
\end{equation}
If the small-$p$ behavior of solution of the previous equation that is well-behaved as $p\rightarrow \infty$ is
\begin{equation}
Y(p) = Y_0\left[1 - c\,p+{\cal O}(p^{\,2})\right].
\end{equation}
then the 
linear layer width is 
\begin{equation}
\delta_{\rm linear}(r) = \frac{\pi\,|c|\,r}{S^{\,1/3}}.
\end{equation}
Note that Eq.~(\ref{e87}) can only be solved when $1+\tau>0$.

@@

\subsection{Critical Island Widths}
The critical full island width (in $r$) which must be exceeded before the electron temperature is flattened within the
magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
\begin{equation}\label{e64g}
W_{T_e\,k} = 5.07\left(\frac{\chi_e}{\chi_{\parallel\,e}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
\end{equation}
where $\epsilon =r/R_0$, and 
\begin{align}
\chi_{\parallel\,e}&= \frac{\chi_{\parallel\,e}^{\rm brag}\,\chi_{\parallel\,e}^{\rm max}}{\chi_{\parallel\,e}^{\rm brag}+\chi_{\parallel\,e}^{\rm max}},\\[0.5ex]
\chi_{\parallel\,e}^{\rm brag} &= \frac{1.55\,\tau_{ee}\,v_{T\,e}^{\,2}}{1+0.38\,Z_{\rm eff}},\\[0.5ex]
\chi_{\parallel\,e}^{\rm max} &= \frac{2\,R_0\,v_{T\,e}}{n\,s}\,\frac{r_k}{W_{T_e\,k}}.
\end{align}
Equation~(\ref{e64g}) must be solved iteratively for $W_{T_e\,k}/r_k$.

The critical full island width (in $r$) which must be exceeded before the ion temperature is flattened within the
magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
\begin{equation}\label{e64gg}
W_{T_i\,k}= 5.07\left(\frac{\chi_i}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
\end{equation}
where $\chi_i(r)$ is the perpendicular ion energy diffusivity profile, 
\begin{align}
\chi_{\parallel\,i}&= \frac{\chi_{\parallel\,i}^{\rm brag}\,\chi_{\parallel\,i}^{\rm max}}{\chi_{\parallel\,i}^{\rm brag}+\chi_{\parallel\,i}^{\rm max}},\\[0.5ex]
\chi_{\parallel\,i}^{\rm brag} &= 1.95\,\tau_{ii}\,v_{T\,i}^{\,2},\\[0.5ex]
\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{T_i\,k}}.
\end{align}
Equation~(\ref{e64gg}) must be solved iteratively for $W_{T_i\,k}/r_k$.

The critical full island width (in $r$) which must be exceeded before the electron density is flattened within the
magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
\begin{equation}\label{e64ggg}
W_{n_e\,k}= 5.07\left(\frac{D_\perp}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
\end{equation}
where 
\begin{align}
\chi_{\parallel\,i}&= \frac{\chi_{\parallel\,i}^{\rm brag}\,\chi_{\parallel\,i}^{\rm max}}{\chi_{\parallel\,i}^{\rm brag}+\chi_{\parallel\,i}^{\rm max}},\\[0.5ex]
\chi_{\parallel\,i}^{\rm brag} &= 1.95\,\tau_{ii}\,v_{T\,i}^{\,2},\\[0.5ex]
\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{n_e\,k}}.
\end{align}
Equation~(\ref{e64ggg}) must be solved iteratively for $W_{n_e\,k}/r_k$.

\subsection{Resonant Plasma Response Model}
Let ${\mit\chi}_k= R_0\,B_0\,\hat{\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$, and $E_{kk'}=\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$,
where  $\hat{\chi}_k>0$, $\zeta_k$, $\hat{E}_{kk}'>0$, and $\xi_{kk'}$ are all real quantities. Furthermore,
let $X_k= \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k= \hat{\mit\Psi}_k\,\sin\varphi_k$. The resonant plasma response model at the 
$k$th resonant surface takes the form
\begin{align}\label{e21}
\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
+\hat{\varpi}_k\,Y_k\right)&= f_k\,X_k+ \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'})\nonumber\\[0.5ex] &\phantom{=}+ {\mit\Sigma}_{kw}\,U_k + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k,\\[0.5ex]
\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
&= f_k\,Y_k + \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
+\sin\xi_{kk'}\,X_{k'}) \nonumber\\[0.5ex]
&\phantom{=}+ {\mit\Sigma}_{kw}\,V_k+ \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k,\label{e22}\\[0.5ex]
\hat{\tau}_w\,\frac{dU_k}{d\hat{t}} &={\mit\Delta}_{kw}\, U_k+ {\mit\Sigma}_{kw}\,X_k,\\[0.5ex]
\hat{\tau}_w\,\frac{dV_k}{d\hat{t}} &={\mit\Delta}_{kw}\, V_k+ {\mit\Sigma}_{kw}\,Y_k,
\end{align}
where
\begin{align}\label{e23}
\hat{W}_k &=\frac{{\cal I}\,W_k}{2\,r_k}=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
{\cal S}_k&=\frac{\tau_R(r_k)}{\tau_A},\\[0.5ex]
\tau_A &= \left[\frac{\mu_0\,\rho(0)\,r_{100}^{\,2}}{B_0^{\,2}}\right]^{1/2},\\[0.5ex]
\hat{\tau}_w &= \frac{\tau_w}{\tau_A},\\[0.5ex]
f_k &=f_{b\,k}+f_{c\,k} + f_{p\,k} + f_{w\,k} + f_{s\,k},
\end{align}
Here, ${\cal I} = 0.8227$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, $\hat{t}=t/\tau_A$, and $\rho(r)$ is the plasma
mass density profile.

The perturbed bootstrap current terms take the form
\begin{align}
f_{b\,k} &= f_{b\,e\,k}+f_{b\,i\,k},\\[0.5ex]
f_{b\,e\,k} &= \alpha_{b\,e\,k}\left(f_{b\,T_e\,k} + f_{b\,n_e\,k}\right),\\[0.5ex]
f_{b\,i\,k} &= \alpha_{b\,i\,k}\left(f_{b\,T_i\,k} + f_{b\,n_i\,k}\right),\\[0.5ex]
f_{b\,T_e\,k}&=\left(\frac{\eta_e}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_e\,k}^{\,2}+\hat{\rho}_{\theta\,e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,n_e\,k}&=\left(\frac{1}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_i\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},
\end{align}
where
\begin{align}
\alpha_{b\,e\,k} &= -2\,{\cal I}\,I_g\left(\frac{\omega_{\ast\,e}+\omega_{{\rm nc}\,e}}{\omega_\beta}\right)_{r_k},\\[0.5ex]
\alpha_{b\,i\,k} &= 2\,{\cal I}\,I_g\left[\frac{(n_i/n_e)\left(\omega_{\ast\,i}+\omega_{{\rm nc}\,i}\right)+(Z_I\,n_I/n_e)\left(\omega_{\ast\,I}+\omega_{{\rm nc}\,I}\right)}{\omega_\beta}\right]_{r_k},\\[0.5ex]
\omega_{\beta}(r)&= \frac{s\,g\,B_0}{\mu_0\,n_e\,e\,R_0^{\,2}\,q},\\[0.5ex]
\hat{W}_{T_e\,k} &=\frac{{\cal I}\,W_{T_e\,k}}{2\,r_k} ,\\[0.5ex]
\hat{W}_{T_i\,k} &= \frac{{\cal I}\,W_{T_i\,k}}{2\,r_k},\\[0.5ex]
\hat{W}_{n_e\,k} &= \frac{{\cal I}\,W_{n_e\,k}}{2\,r_k},\\[0.5ex]
\hat{\rho}_{\theta\,e\, k} &= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
\hat{\rho}_{\theta\,i\,k} &= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},
\end{align}
and $I_g = 1.58$.

>>>>

The quantities ${\mit\Delta}_k^{pw}$ and ${\mit\Sigma}_k^{\,pw}$
are defined as 
\begin{align}
{\mit\Delta}_k^{nw}&= \lim_{\delta\rightarrow 0}
\left[\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k+\delta}
- \left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k-\delta}\right],\\[0.5ex]
{\mit\Sigma}_k^{\,pw} &= \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k+\delta}+ \left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k-\delta}
-2\,A_k\,(1+\ln\delta)\right].
\end{align}
Here, $\psi_{pw}(r)$ is a solution of the cylindrical tearing mode equation that is well-behaved at $r=0$,
continuous at $r=r_k$, and satisfies 
\begin{equation}
\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_{100}} = -m\left[\frac{1+(r_{100}/r_w)^{\,2m}}{1-(r_{100}/r_w)^{\,2m}}\right].
\end{equation}
It is also helpful to define
\begin{align}
{\mit\Sigma}_{kw} &= \frac{2m\,(r_{100}/r_w)^{\,m}}{1-(r_{100}/r_w)^{\,2m}}\,\frac{\psi_{pw}(r_{100})}{\psi_{pw}(r_k)},\\[0.5ex]
{\mit\Delta}_{kw} &= -\left(\frac{{\mit\Sigma}_{kw}^{\,2}}{{\mit\Delta}^{nw}_k-{\mit\Delta}^{pw}_k}\right),\\[0.5ex]
B_k &= -\left(\frac{r^{\,2}\,q\,\hat{J}_\phi''}{s}\right)_{r_k},
\end{align}
where $\hat{J}_\phi'' \equiv d^{\,2}\hat{J}_\phi/dr^{\,2}$.

\section{Neoclassical Physics}\label{appb}
\subsection{Plasma Species}\label{a3}
The plasma is assumed to consist of three (charged) species (with Maxwellian distribution functions); namely,  electrons ($e$), majority ions ($i$), and impurity ions
($I$).  The charges of the  three species are $e_e=-e$, $e_i= e$, and $e_I=Z_I\,e$, respectively, where
$e$ is the magnitude of the electron charge. 
Quasi-neutrality demands that
$n_e= n_i+ Z_I\,n_I$, where $n_a(r)$ is the species-$a$ number density. 
 Let 
$\alpha_I(r) =Z_I\,(Z_{\rm eff}-1)/(Z_I-Z_{\rm eff})$,
where 
$Z_{\rm eff}(r) = (n_i+Z_I^{\,2}\,n_I)/n_e$
is the effective ion charge number. It follows that
$n_i/n_e = (Z_I-Z_{\rm eff})/(Z_I-1)$
and
$n_I/n_e= (Z_{\rm eff}-1)/[Z_I\,(Z_I-1)]$. Finally, let $Z_{{\rm eff}\,i}= (Z_I-Z_{\rm eff})/(Z_I-1)$, and
$Z_{{\rm eff}\,I}=Z_I\,(Z_{\rm eff}-1)/(Z_I-1)$. Note that $Z_{\rm eff}= Z_{{\rm eff}\,i}+ Z_{{\rm eff}\,I}$.

@@

\section{Plasma Response in Inner Region}
\subsection{Linear Layer Widths}\label{linear}
Let
\begin{align}
\tau_R(r) &= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{ee},\\[0.5ex]
\sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
\tau_H(r) &= \frac{R_0}{B_0\,g}\,\frac{\sqrt{\mu_0\,\rho}}{n\,s},\\[0.5ex]
\rho(r)&= m_i\left[n_i(r) + n_b(r)\right] + m_I\,n_I(r),\\[0.5ex]
\tau_E(r) &= \frac{r^{\,2}}{D_\perp + (2/3)\,\chi_e},\\[0.5ex]
\tau_M(r) &= \frac{R_0^{\,2}\,q^{\,2}}{\chi_\phi},\\[0.5ex]
\rho_s (r)&= \frac{\sqrt{m_i\,T_e}}{e\,B_0\,g},\\[0.5ex]
\tau(r)& = -\frac{\omega_{\ast\,i}}{\omega_{\ast\,e}},\\[0.5ex]
S(r) &= \frac{\tau_R}{\tau_H},\\[0.5ex]
P_M(r) &= \frac{\tau_R}{\tau_M},\\[0.5ex]
P_E(r) &= \frac{\tau_R}{\tau_E},\\[0.5ex]
D(r)&= \frac{5}{3}\,S^{\,1/3}\,\frac{\rho_s}{r},\\[0.5ex]
Q_E(r)&= S^{\,1/3}\,n\,\omega_E\,\tau_H,\\[0.5ex]
Q_{e,i}(r)&= -S^{\,1/3}\,n\,\omega_{\ast\,e,i}\,\tau_H
\end{align}
Here, $\chi_e(r)$, $D_\perp(r)$, and $\chi_\phi(r)$ are the perpendicular electron energy, particle,
and toroidal momentum diffusivity profiles, respectively. Moreover, $n_b(r)$ is the number density of fast (as opposed to thermal) majority ions. 
The constant-$\psi$ linear layer width is determined from the solution of
\begin{equation}\label{e87}
\frac{d^{\,2}\,Y}{dp^{\,2}} -\left[\frac{-Q_E\,(Q_E-Q_i)+{\rm i}\,(Q_E-Q_i)\,(P_M+P_E)\,p^{\,2}+
P_M\,P_E\,p^{\,4}}
{{\rm i}\,(Q_E-Q_e) +\{P_E + {\rm i}\,(Q_E-Q_i)\,D^{\,2}\}\,p^{\,2}+(1+\tau)\,P_M\,D^{\,2}\,p^{\,4}}
\right] p^{\,2}\, Y = 0.
\end{equation}
If the small-$p$ behavior of solution of the previous equation that is well-behaved as $p\rightarrow \infty$ is
\begin{equation}
Y(p) = Y_0\left[1 - c\,p+{\cal O}(p^{\,2})\right].
\end{equation}
then the 
linear layer width is 
\begin{equation}
\delta_{\rm linear}(r) = \frac{\pi\,|c|\,r}{S^{\,1/3}}.
\end{equation}
Note that Eq.~(\ref{e87}) can only be solved when $1+\tau>0$.

@@

\subsection{Critical Island Widths}
The critical full island width (in $r$) which must be exceeded before the electron temperature is flattened within the
magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
\begin{equation}\label{e64g}
W_{T_e\,k} = 5.07\left(\frac{\chi_e}{\chi_{\parallel\,e}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
\end{equation}
where $\epsilon =r/R_0$, and 
\begin{align}
\chi_{\parallel\,e}&= \frac{\chi_{\parallel\,e}^{\rm brag}\,\chi_{\parallel\,e}^{\rm max}}{\chi_{\parallel\,e}^{\rm brag}+\chi_{\parallel\,e}^{\rm max}},\\[0.5ex]
\chi_{\parallel\,e}^{\rm brag} &= \frac{1.55\,\tau_{ee}\,v_{T\,e}^{\,2}}{1+0.38\,Z_{\rm eff}},\\[0.5ex]
\chi_{\parallel\,e}^{\rm max} &= \frac{2\,R_0\,v_{T\,e}}{n\,s}\,\frac{r_k}{W_{T_e\,k}}\label{e64d}
\end{align}
Equations~(\ref{e64g})--(\ref{e64d}) must be solved iteratively for $W_{T_e\,k}/r_k$.

The critical full island width (in $r$) which must be exceeded before the ion temperature is flattened within the
magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
\begin{equation}\label{e64gg}
W_{T_i\,k}= 5.07\left(\frac{\chi_i}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
\end{equation}
where $\chi_i(r)$ is the perpendicular ion energy diffusivity profile, 
\begin{align}
\chi_{\parallel\,i}&= \frac{\chi_{\parallel\,i}^{\rm brag}\,\chi_{\parallel\,i}^{\rm max}}{\chi_{\parallel\,i}^{\rm brag}+\chi_{\parallel\,i}^{\rm max}},\\[0.5ex]
\chi_{\parallel\,i}^{\rm brag} &= 1.95\,\tau_{ii}\,v_{T\,i}^{\,2},\\[0.5ex]
\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{T_i\,k}}.\label{e64rr}
\end{align}
Equations~(\ref{e64gg})--(\ref{e64rr}) must be solved iteratively for $W_{T_i\,k}/r_k$.

The critical full island width (in $r$) which must be exceeded before the electron density is flattened within the
magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
\begin{equation}\label{e64ggg}
W_{n_e\,k}= 5.07\left(\frac{D_\perp}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
\end{equation}
where 
\begin{align}
\chi_{\parallel\,i}&= \frac{\chi_{\parallel\,i}^{\rm brag}\,\chi_{\parallel\,i}^{\rm max}}{\chi_{\parallel\,i}^{\rm brag}+\chi_{\parallel\,i}^{\rm max}},\\[0.5ex]
\chi_{\parallel\,i}^{\rm brag} &= 1.95\,\tau_{ii}\,v_{T\,i}^{\,2},\\[0.5ex]
\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{n_e\,k}}.\label{e64fff}
\end{align}
Equations~(\ref{e64ggg})--(\ref{e64fff}) must be solved iteratively for $W_{n_e\,k}/r_k$.

\subsection{Resonant Plasma Response Model}
Let ${\mit\chi}_k= R_0\,B_0\,\hat{\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$, and $E_{kk'}=\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$,
where  $\hat{\chi}_k>0$, $\zeta_k$, $\hat{E}_{kk}'>0$, and $\xi_{kk'}$ are all real quantities. Furthermore,
let $X_k= \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k= \hat{\mit\Psi}_k\,\sin\varphi_k$. The resonant plasma response model at the 
$k$th resonant surface takes the form
\begin{align}\label{e21}
\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
+\hat{\varpi}_k\,Y_k\right)&= f_k\,X_k+ \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'})\nonumber\\[0.5ex] &\phantom{=}+ {\mit\Sigma}_{kw}\,U_k + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k,\\[0.5ex]
\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
&= f_k\,Y_k + \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
+\sin\xi_{kk'}\,X_{k'}) \nonumber\\[0.5ex]
&\phantom{=}+ {\mit\Sigma}_{kw}\,V_k+ \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k,\label{e22}\\[0.5ex]
\hat{\tau}_w\,\frac{dU_k}{d\hat{t}} &={\mit\Delta}_{kw}\, U_k+ {\mit\Sigma}_{kw}\,X_k,\\[0.5ex]
\hat{\tau}_w\,\frac{dV_k}{d\hat{t}} &={\mit\Delta}_{kw}\, V_k+ {\mit\Sigma}_{kw}\,Y_k,
\end{align}
where
\begin{align}\label{e23}
\hat{W}_k &=\frac{{\cal I}\,W_k}{2\,r_k}=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
{\cal S}_k&=\frac{\tau_R(r_k)}{\tau_A},\\[0.5ex]
\tau_A &= \left[\frac{\mu_0\,\rho(0)\,r_{100}^{\,2}}{B_0^{\,2}}\right]^{1/2},\\[0.5ex]
\hat{\tau}_w &= \frac{\tau_w}{\tau_A},\\[0.5ex]
f_k &=f_{b\,k}+f_{c\,k} + f_{p\,k} + f_{w\,k} + f_{s\,k},
\end{align}
Here, ${\cal I} = 0.8227$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, and $\hat{t}=t/\tau_A$. Note that the EPEC resonant plasma response model interpolates smoothly
between the linear regime and the
nonlinear Rutherford regime. The linear regime corresponds to $\hat{W}_k\ll\hat{\delta}_k$, whereas the nonlinear
region corresponds to $\hat{W}_k\gg\hat{\delta}_k$.

The perturbed bootstrap current terms in the response model take the form
\begin{align}
f_{b\,k} &= f_{b\,e\,k}+f_{b\,i\,k},\\[0.5ex]
f_{b\,e\,k} &= \alpha_{b\,e\,k}\left(f_{b\,T_e\,k} + f_{b\,n_e\,k}\right),\\[0.5ex]
f_{b\,i\,k} &= \alpha_{b\,i\,k}\left(f_{b\,T_i\,k} + f_{b\,n_i\,k}\right),\\[0.5ex]
f_{b\,T_e\,k}&=\left(\frac{\eta_e}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_e\,k}^{\,2}+\hat{\rho}_{\theta\,e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,n_e\,k}&=\left(\frac{1}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_i\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},
\end{align}
where
\begin{align}
\alpha_{b\,e\,k} &= -2\,{\cal I}\,I_g\left(\frac{\omega_{\ast\,e}+\omega_{{\rm nc}\,e}}{\omega_\beta}\right)_{r_k},\\[0.5ex]
\alpha_{b\,i\,k} &= 2\,{\cal I}\,I_g\left[\frac{(n_i/n_e)\left(\omega_{\ast\,i}+\omega_{{\rm nc}\,i}\right)+(Z_I\,n_I/n_e)\left(\omega_{\ast\,I}+\omega_{{\rm nc}\,I}\right)}{\omega_\beta}\right]_{r_k},\\[0.5ex]
\omega_{\beta}(r)&= \frac{s\,g\,B_0}{\mu_0\,n_e\,e\,R_0^{\,2}\,q},\\[0.5ex]
\hat{W}_{T_e\,k} &=\frac{{\cal I}\,W_{T_e\,k}}{2\,r_k} ,\\[0.5ex]
\hat{W}_{T_i\,k} &= \frac{{\cal I}\,W_{T_i\,k}}{2\,r_k},\\[0.5ex]
\hat{W}_{n_e\,k} &= \frac{{\cal I}\,W_{n_e\,k}}{2\,r_k},\\[0.5ex]
\hat{\rho}_{\theta\,e\, k} &= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
\hat{\rho}_{\theta\,i\,k} &= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},
\end{align}
and $I_g = 1.58$.
